---
title: "How Much Money Can You Make"
author: "Heming and Kit"
date: "Winter 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
```
```{r}
library("RColorBrewer")
library("paletteer")
```
```{r}
prof_salary <-
  readr::read_csv("salaries_prof.csv")
```

## What is our project about?
We collected a dataset about the salary of professors in college.
It is from ""

This dataset includes:

- Rank: Professor, Assistant Professor, and Associate Professor
- Discipline: A and B
- Years since Phd
- Years since Service
- Salary

## Have a look
```{r}
prof_salary %>% 
  skimr::skim()
```

## Make it tidy
```{r}
prof_salary_tidy <-prof_salary %>% 
  dplyr::rename(
    Participants = X1,
    Rank = rank,
    Discipline = discipline,
    Yrs_since_PhD = yrs.since.phd,
    Yrs_service = yrs.service,
    Sex = sex,
    Salary = salary)
prof_salary_tidy
```

## Average Salary of Each Rank
```{r}
Mean_Salary <- prof_salary_tidy %>% 
  group_by(Rank) %>% 
  summarize(Mean_Salary=(mean(Salary, na.rm = TRUE)))
Mean_Salary
```

##Plot of Average Salary of Each Rank
```{r}
Mean_Salary %>% 
  ggplot(aes(x=Rank, y=Mean_Salary,fill=Rank))+
  geom_bar(stat="identity", alpha=0.9, color="black")+
  labs(title = "Mean Salary By Rank of Professors",
       x = "Rank",
       y = "Mean Salary")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_fill_brewer(palette = "Dark2")
```


## Interesting Plots - Salary Distribution
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Salary))+
  geom_histogram(aes(y = ..density..), fill="darkgreen", alpha=0.8, color="black")+
  geom_density(color="orange")
```


## Plots Associated with Gender
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Rank, fill=Sex))+
  geom_bar(alpha=0.9, color="black", position = position_fill(), stat = "count")+
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Gender Distribution within the Ranks of Professors",
       x = "Rank",
       y = "# of Individuals")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_fill_brewer(palette = "Dark2")
```


## Plots Associated with Gender
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Salary, fill=Sex))+
  geom_density(alpha=0.65)+
  labs(title = "Salary in Relation to Gender",
       x = "Salary",
       y = "Density")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_fill_brewer(palette = "Dark2")
```

## Average Salary of Each Gender
```{r}
Mean_Salary_Gender <- prof_salary_tidy %>% 
  group_by(Sex) %>% 
  summarize(Mean_Salary=(mean(Salary, na.rm = TRUE)))
Mean_Salary_Gender
```


## Plots Associated with Gender
```{r}
Mean_Salary_Gender %>% 
  ggplot(aes(x=Sex, y=Mean_Salary,fill=Sex))+
  geom_bar(stat="identity", alpha=0.9, color="black")+
  labs(title = "Mean Salary By Gender",
       x = "Gender",
       y = "Mean Salary")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_fill_brewer(palette = "Dark2")
```


## Plots Associated with Gender
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Salary, fill=Sex))+
  geom_density(alpha=0.65)+
  labs(title = "Salary in Relation to Gender",
       x = "Salary",
       y = "Density")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_fill_brewer(palette = "Dark2")
```


## Plots Associated with Gender and Discipline
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Discipline, y=Salary, fill=Sex))+
  geom_boxplot(alpha=0.9, color="black")+
  labs(title = "Mean Salary By Discipline",
       x = "Discipline",
       y = "Salary")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_fill_brewer(palette = "Dark2")
```


## Plots Associated with Years
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Yrs_since_PhD, y=Salary, color=Rank))+
  geom_point(size=0.9)+
  facet_wrap(~Rank)+
  geom_smooth(method=lm, se=TRUE)+
  labs(title = "Salary vs. Years Since PhD",
       x = "Years Since PhD",
       y = "Salary")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_colour_brewer(palette = "Dark2")
```


## Plots Associated with Years
```{r}
prof_salary_tidy %>% 
  ggplot(aes(x=Yrs_service, y=Salary, color=Rank))+
  geom_point(size=0.9)+
  facet_wrap(~Rank)+
  geom_smooth(method=lm, se=TRUE)+
  labs(title = "Salary vs. Years Service",
       x = "Years Service",
       y = "Salary")+
  theme(plot.title=element_text(size=18, face="bold", hjust = 0.5),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12))+
  scale_colour_brewer(palette = "Dark2")
```


## Conclusion

- Males have advantage over females being professors
- If you are a teaching faculty, you should try to get promoted
- Discipline B makes more money than discipline A